---
title: "Homework 5"
author: "Lorraine Kwok"
date: "November 5, 2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(10)
```

## Problem 1

The following code chunk generates missing values in the `iris_with_missing` dataframe.

```{r}
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

The following code chunk shows a function that will replace the missing values in each variable. For numeric variables, the missing values will be replaced with column mean. For character variables, the  

```{r}
output = vector("list", length = 5)

iris_filling = function(x) {
  
  if (is.numeric(x)) {
    x = replace_na(x, mean(x, na.rm = TRUE))
  }
  else if (is.character(x)) {
    x = replace_na(x, "virginica")
  }
  
}

output = map(iris_with_missing, iris_filling)
```

## Problem 2

This code chunk creates a dataframe that consists of the file names and converts it into a vector.

```{r}
df = list.files(pattern = "*.csv")

vec_file = str_c(df)
```

This code chunk creates a function that reads in data for each subject from each individual csv file and saves the weekly observations as a new varaible in the dataframe. 

```{r}

for (i in length(df):1) {
  output[[i]] = read_csv(vec_file[[i]])
}

output = cbind(vec_file, map_df(vec_file, read_csv))
```

This code chunk tidies the resulting dataframe obtained from the for loop. 

```{r}
study_df = 
  output %>%
  separate(vec_file, c("control_arm", "subject_id")) %>%
  separate(subject_id, c("subject_id", "csv"), ".csv") %>%
  select(-csv) %>%
  mutate(control_arm =
           recode(control_arm, con = "control", exp = "experimental")) %>%
  pivot_longer(cols = starts_with("week_"),
               names_to = "week",
               values_to = "obs")
```

The following code chunk creates a spaghetti plot that shows the observations for each subject over time. 

```{r}
study_df %>%
  group_by(control_arm, subject_id) %>%
  ggplot(aes(x = week, y = obs, group = subject_id, color = control_arm)) +
  geom_path() + 
  labs(title = "Figure 1. Study observations for each subject over time",
       x = "Week",
       y = "Observations")
```

Based on the spaghetti plot, subjects in the control arm seem to have lower numbers of observations compared to those in the experimental arm.There is a bit of overlap between the two study arms between 1.25 and 3.75 numbers of observations. 

## Problem 3

This code chunk creates a function that simulates data for a simple linear regression for a sample size of 30, β0 of 2 and β1 of 0 and fits the regression model.

```{r}
sim_regression = function(n = 30, beta0 = 2, beta1 = 0) {
  
  sim_data = tibble(
    x1 = rnorm(30, 0, 1),
    y = beta0 + beta1 * x1 + rnorm(30, 0, 50)
  )
  
  ls_fit = lm(y ~ x1, data = sim_data) %>%
    broom::tidy()
}
```

The following code chunk allows us to run `sim_regression()` 10000 times and generates a dataframe reporting each β̂1 and p-value.There is also code that tidies up some of these data. 

```{r}
output2 = vector("list", 10000)

for (i in 1:10000) {
  output2[[i]] = sim_regression(n)
}
  
sim_results =
  rerun(10000, sim_regression()) %>%
  bind_rows(output2) %>%
  select(term, p.value) %>%
  filter(term == "x1") %>%
  mutate(term = str_replace(term, "x1", "beta1_hat"))
```

